% Created 2019-08-20 Tue 15:29
% Intended LaTeX compiler: pdflatex
\documentclass[bigger]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{listings}
\author{Hung Dang}
\date{\textit{<2019-08-20 Tue>}}
\title{ioutils: A blazing fast file I/O library.}
\hypersetup{
    pdfauthor={Hung Dang},
    pdftitle={ioutils: A blazing fast file I/O library.},
    pdflang={English}
}

\begin{document}
\maketitle

% \tableofcontents
\begin{frame}
    \frametitle{Motivations}
    \begin{itemize}
        \pause
    \item Support regular expression pattern matching by default.
        \pause
    \item Can reuse file traversal, reading, and writing algorithms in
        other projects with a minimal effort.
        \pause
    \item Work out of the box in all Linux and macOS environments i.e
        all commands are portable.
        \pause
    \item Add more nuclear weapons to my Emacs setup.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Used packages and tools}
    \begin{itemize}
    \item Packages
        \begin{itemize}
        \item AquaHash
        \item Celero
        \item Clara
        \item doctest
        \item Google benchmark
        \item hyperscan
        \item fmt
        \item utils
        \item boost
        \end{itemize}
    \item Tools
        \begin{itemize}
        \item cmake
        \item perf
        \item strace
        \item clang, bash, python
        \end{itemize}
    \end{itemize}
\end{frame}

% Compile time vs run-time
\begin{frame}
    \frametitle{How can we do more work at compile time?}
    \pause
    \begin{itemize}
    \item Consider the policy-based design.
        \pause
        \begin{quote}
            Policy-based design, also known as policy-based class design or
            policy-based programming, is the term used in Modern C++ Design for a
            design approach based on an idiom for C++ known as policies. It has
            been described as a compile-time variant of the strategy pattern, and
            has connections with C++ template meta-programming. (Wikipedia)
        \end{quote}
    \item Generate code at the compile time for different user constraints.
    \end{itemize}
\end{frame}

% File traversal algorithms
\begin{frame}
    \frametitle{Why do we need to rewrite file traversal algorithms?}
    \begin{itemize}
    \item Can control our resource consumption.
        \pause
    \item Can filter/prune search paths using input constraints.
        \pause
    \item File traversal algorithms
        \begin{itemize}
            \pause
        \item Depth-first search algorithm.
            \pause
        \item Breath-first search algorithm.
        \end{itemize}
    \end{itemize}
\end{frame}

% Output results
\begin{frame}
    \frametitle{How can we display the results fast?}
    \begin{enumerate}
    \item Use C++ iostream
        \pause
        \begin{itemize}
        \item Does not take a segment of a string.
        \end{itemize}
        \pause
    \item Use fmt library
        \pause
        \begin{itemize}
        \item Does not take a segment of a string.
        \end{itemize}
        \pause
    \item Use printf and puts functions.
        \pause
        \begin{itemize}
        \item Does not take a segment of a string.
        \end{itemize}
        \pause
    \item Use low level C APIs
    \end{enumerate}
\end{frame}

% How to read data from a file fast.
\begin{frame}
    \frametitle{What is the fastest way to read data from a file?}
    \begin{enumerate}
    \item Use std::iostream
        \pause
    \item Use memory mapped files.
        \pause
    \item Use fread
        \pause
    \item Use read function to read data in chunks.
        \pause
        \begin{itemize}
        \item This is the fastest way to read the content of a file
            (see Daniel Lemire and Andrew Gallant blogs for detail analysis).
        \end{itemize}
    \end{enumerate}
\end{frame}

% Regular expression matching algorithm
\begin{frame}
    \frametitle{Which regular expression pattern matching library
        should we use?}
    \begin{itemize}
        \pause
    \item std::regex is slow and may not suitable for data intensive
        applications.
        \pause
    \item Use Google re2 or hyperscan if you can because they can offer O(n)
        algorithms for regular expression pattern matching.
    \end{itemize}
\end{frame}

% Portable
\begin{frame}
    \frametitle{How can we make all commands portable?}
    \pause
    \begin{itemize}
    \item Use header only packages or packages that provide
        statically linked libraries.
        \pause
    \item All commands are linked using the -static flag i.e the final
        output of a binary blob.
    \end{itemize}
\end{frame}

% Other constraints
\begin{frame}
    \frametitle{Other constraints}
    \begin{itemize}
        \pause
    \item Reduce the binary size.
        \pause
    \item Use error codes instead of exceptions in the critical code.
    \end{itemize}
\end{frame}

% Benchmark results
\begin{frame}
    \frametitle{Benchmark results}
    \begin{itemize}
    \item fast-find
        \pause
    \item fast-updatedb
        \pause
    \item fast-locate
    \end{itemize}
\end{frame}

% Future work
\begin{frame}
    \frametitle{Future work}
    \begin{itemize}
    \item Support username and group filter.
    \item Support timestamp filter.
    \item Have a better support for symbolic linked paths.
    \end{itemize}
\end{frame}

% Acknowledgments
\begin{frame}
    \frametitle{Acknowledgments}
    \begin{itemize}
    \item Zac Bentley and Tue Ly.
    \item Mia Moretti.
    \item Jared Briskman.
    \end{itemize}
\end{frame}

% Q/A
\begin{frame}
    \frametitle{Q/A}
\end{frame}
\end{document}

% Bibliography
\begin{frame}
    \frametitle{References}
    \begin{thebibliography}{10}
    \bibitem{lemire_blog}[Daniel Lemire blog] https://lemire.me/blog/
    \end{thebibliography}
\end{frame}
